Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-02-06 alloscore_manuscript/alloscore-application-shorter.Rnw

In the wake of the COVID-19 pandemic, researchers have been calling for evaluating infectious disease forecasts through their impact on policy \citep{marshall2023predictions, bilinski_adaptive_2023}.
Historically, the quality of disease forecasts has typically been measured using scores such as root mean square error (RMSE) \citep{papastefanopoulos2020covid}, log score \citep{mcgowan_collaborative_2019}, or weighted interval score (WIS) \citep{bracher2021evaluating}.  These scores can be interpreted as measuring how well the forecast corresponds to the observed disease outcome.
However, as we show in this paper, these scores often do not clearly measure the value of a forecast in the context of a specific decision.
While these ideas have received little attention in the context of infectious disease forecasting, the results are well known from other fields, such as economics and finance, supply chain management, and meteorology.

>>>>

In the wake of the COVID-19 pandemic, researchers have been calling for evaluating infectious disease forecasts in ways that align more specifically with how forecasts can be used to inform policy decisions \citep{marshall2023predictions, bilinski_adaptive_2023}.
Historically, the quality of disease forecasts has typically been measured using scores such as root mean square error (RMSE) \citep{papastefanopoulos2020covid}, log score \citep{mcgowan_collaborative_2019}, or weighted interval score (WIS) \citep{bracher2021evaluating}.
These scores can be interpreted as measuring how well the forecast corresponds to the observed disease outcome but often do not clearly measure the value of a forecast in the context of a specific decision, a result that is well known from other fields, such as economics and finance, supply chain management, and meteorology.
However, as we show in this paper, it is possible to construct formal methods for evaluating forecasts that are directly and uniquely tied to policy decisions (in our hypothetical setting, a question of resource allocation).
Furthermore, such scores can illuminate important features of forecasts, and their value as decision-making inputs, that can be missed by traditional accuracy measures.
